\newpage
\begin{section}{Step-by-step use of OASIS}
\label{sec_step}
To use OASIS for coupling independent models, one has to follow these
steps:
\begin{enumerate}
\item Familiarize yourself with a toy coupling by running a toy
coupled model with either the PIPE technique 
(see directory {\tt /toypipe}), the SIPC technique 
(see directory {\tt /toysvipc}), the CLIM technique
(see directory {\tt /toyclim}), or the GMEM technique 
(see directory {\tt /toysxgmem}).
\item Identify for the present coupling the fields exchanged from 
each model to another model.
\item Define for each coupling field the analyses required to go from 
one model to the other, that will be performed by OASIS (refer to 
\ref{subsec_analyses}).
\item Define all coupling parameters (time strategy, communication 
technique, etc. - see \ref{subsubsec_general}).
\item With 2., 3. and 4., prepare OASIS input file {\em namcouple}
(see \ref{subsec_input}). Two examples of {\em namcouple} are given 
in appendix \ref{app_namcouple} and one can also find a file example 
{\tt /src/namcouple}.

\item Generate all auxiliary data files (see \ref{subsec_data}).

\item Adjust OASIS parameters in {\tt src/parameter.h} (see 
\ref{subsec_parameters}).

\item Compile OASIS main, communication and interpolation libraries used 
in the coupling. Note that some machines (like the Fujitsu VPP) do not 
support undefined external references; in that case you may have to compile 
and link the {\tt lib/dummy} libraries of the communication techniques 
NOT used in the coupling (see the makefiles in directory {\tt tools}
for examples). Note that to run with the CLIM technique on a CRAY and
avoid undefined external references, you
need to compile and link the routines {\tt dummypipe.f}, 
{\tt dummysvipc.f}, and {\tt svipcdummy.c} in {\tt lib/dummy}; to
run with the CLIM technique on another machine than a CRAY and
avoid undefined external references, you also
need to need to compile and link with the same routines + 
{\tt lib/dummy/dummysrc.f} (see {\tt /tools/Makefile\_clim}).
 
\item Make the appropriate modifications in the models in order to allow
the exchange of the coupling fields with the chosen communication technique.
For the PIPE, CLIM, SIPC or GMEM communication techniques, refer 
to the toy model given in respectively the /toypipe, /toyclim, /toysvipc 
or /toysxgmem directory.

\item Compile the models.

\item Launch the coupled simulation.

\end{enumerate}

 If you need extra help, we will be happy to
hear from you (oasishelp@cerfacs.fr)!



\end{section}

